### 2019-07-24 manuscript_clean.Rmd
VCV analysis results section

In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools]. Since the character data contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset. This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters. In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip]. In order to study correlations between the rates of evolution of each character, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv). When fitting all covariance terms simultaneously, we selected the largest set of characters that would allow the analysis to run without computational singularities. This excluded many of the morphometric characters which are linearly dependent on other characters. Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states. To test whether phenotypic integration changes across selective regimes determined by the reconstrcuted feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes. These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset. All the pairwise analyses were carried out transforming abstent states to zeroes. Finally, we compared regime-specific variance covariance matrices to the general matrix to identify the changes in character dependence unique to each regime (see Appendix 20).

@@

>>>>

In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools]. Since the character data contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset. This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters. In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip]. In order to study correlations between the rates of evolution of each character, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv). When fitting all covariance terms simultaneously, we selected the largest set of characters that would allow the analysis to run without computational singularities. This excluded many of the morphometric characters which are linearly dependent on other characters. Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states. To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes. These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset. All the pairwise analyses were carried out transforming absent states to zeroes. Finally, we compared regime-specific variance covariance matrices to the general matrix to identify the changes in character dependence unique to each regime (see Appendix 20).

@@

The variance covariance matrices (Appendix 20.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig. \@ref(figure8)a. However, this analysis reveals more clearly the diagonal blocks that constitute integration modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block. These results were not very sensitive to transformation of inapplicable states and taxon sampling. When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 20.4), we found that about half (53%) of the character pairs presented different correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.

When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 20.5-20.6). For example, haploneme and heteroneme lengths hold a strong positive correlation under a crustacean specialist regime, which reverses to a strong negative relationship in fish specialists. Gelatinous specialist correlations cannot be effectively interpreted since they correspond to a monotypic branch (*Apolemia*) which has lost many characters. Under a generalist trophic regime, rhopaloneme width becomes negatively correlated with elastic strand width, haploneme width, heteroneme length, heteroneme shaft size, and positively correlated with involucrum length. Desmoneme length also shows a unique suite of negative correlations under the generalist regime, such as with desmoneme width, haploneme and heteroneme length, heteroneme shaft width, and pedicle width, but again a strong positive correlation with involucrum. This is consistent with the characteristic morphology of *Agalma* and *Athorybia* tentilla and nematocysts. Soft bodied specialists (fish and gelatinous prey) present a large suite of unique negative correlations corresponding to the different ways in which nematocyst types and structures are reduced. Both crustacean specialist regimes (large and small) share positive correlations of haploneme and elastic strand widths with other characters. however, small crustacean specialists differ from large crustacean specialists by their negative correlation between cnidoband length and heteroneme number, involucrum length and pedicle width, involucrum length and cnidoband free length, and involucrum length with heteroneme volume. In addition, tentacle and pedicle width become strongly positively correlated with desmoneme and rhopaloneme sizes when specializing on smaller prey, while showing a strong opposite relationship in large crustacean specialists.
